### 2016-10-01 BF_correctness.tex
Spell check
changes to BF

In $\game{3}$, we modify the $\HashOracle$ oracle so that on query~$\qry_x$ it returns all of the~$k$ values that previously would have required calls $\HashOracle(1,\qry_y),\HashOracle(2,\qry_y),\ldots,\linebreak\HashOracle(k,\qry_y)$.  This results in adversary getting $(k-1)$ hash values ``for free'', as we charge the adversary only for a single query.  We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\Hash(\qry_x)$ rather than~$k$ such calls.  
We do this so that we can assume that a call~$\HashOracle(\qry_x)$ is pointless after a~$\TestOracle(\qry_x)$ call, and this will aid us in subsequent games.  \fixme{for BF proof, this actually does more, it makes a hash query as good as a test query, because~$M$ is public.}  Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.

Game~$\game{4}$ contains some important changes from game~$\game{3}$, but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A) = 1}$.  To begin, in game~$\game{4}$ we sample an $r$-subset of indices from~$\{1,2,\ldots,q_H+q_T\}$.  (We will see why, shortly.)  Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes its answer directly, but instead refers to a new table~$\mathrm{Ans}[x]$ which is populated upon calls to the $\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call; otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly the values that~$\TestOracle(\qry_x)$ would have returned in the previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$.  (We no longer need to maintain the table~$T$ because hash values are only determined by~$\HashOracle$ calls, and these are never repeated under our no-pointless-query assumption.)  It then computes the answer that~$\TestOracle(\qry_x)$ would return, in game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use by~$\TestOracle$.  The $\HashOracle$ oracle also introduces a query counter~$c$, which is incremented whenever~$\HashOracle$ is called, either directly by~$A$ or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$ where~$\mathrm{Ans}[x]$ had not been previously defined by a~$\HashOracle(\qry_x)$ call.  \fixme{for BF proof, we can assume that $\TestOracle(\qry_x)$ is never made after a~$\HashOracle(\qry_x)$ call, because~$M$ is public.  And vice versa.  So the maximum value of~$c = q_T + q_H$.}  (Note that the maximum value of~$c$ is $q_T + q_H$.)  The set~$\calI$ contains a set of~$r$ distinct values from $\{1,2,\ldots,q_T+q_H\}$ and, intuitively, these are the game's ``guesses'' at the $\HashOracle$ queries that will result in a correctness error.  If these~$r$ guesses are incorrect, then a boolean flag~$\bad$ is set, although in game~$\game{4}$ the value of~$\bad$ has no effect on the games execution; in particular, $\game{4}$ does \emph{not} contain the boxed ``Return 0'' statement.

Games~$\game{4}$ and $\game{5}$ are identical except for this boxed statement.  In particular, game~$\game{5}$ returns 1 exactly when~$\game{4}$ would return 1 \emph{and} the boolean~$\bad$ would have remained false in~$\game{4}$.   This implies that~$game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
$\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.

@@

Ret $v$

@@

Ret $\left(v_1,\ldots,v_k\right)$

@@

$c \gets c + 1$\\

@@

>>>>

In $\game{3}$, we modify the $\HashOracle$ oracle so that on query~$\qry_x$ it returns all of the~$k$ values that previously would have required calls $\HashOracle(1,\qry_y),\HashOracle(2,\qry_y),\ldots,\linebreak\HashOracle(k,\qry_y)$.  This results in adversary getting $(k-1)$ hash values ``for free'', as we charge the adversary only for a single query.  We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\Hash(\qry_x)$ rather than~$k$ such calls.  We do this so that we can assume that a call~$\HashOracle(\qry_x)$ is pointless after a~$\TestOracle(\qry_x)$ call, and this will aid us in subsequent games.  \fixme{for BF proof, this actually does more, it makes a hash query as good as a test query, because~$M$ is public.} Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.  We assume from Game~$\game{3}$ and on that $\Rep$ is also appropriately modifed for the new behavior of~$\HashOracle$.

Game~$\game{4}$ contains some important changes from game~$\game{3}$,
but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A)
  = 1}$.  To begin, in game~$\game{4}$ we sample an $r$-subset of
indices from~$\{1,2,\ldots,q_H+q_T\}$.  (We will see why, shortly.)
Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes
its answer directly, but instead refers to a new
table~$\mathrm{Ans}[x]$ which is populated upon calls to the
$\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is
undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call;
otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which
contains exactly the values that~$\TestOracle(\qry_x)$ would have
returned in the previous game.  The $\HashOracle$ oracle, on
input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in
$\game{3}$.  
%(We no longer need to maintain the table~$T$ because hash values are
%only determined by~$\HashOracle$ calls, and these are never repeated
%under our no-pointless-query assumption.)  
It then computes the answer that~$\TestOracle(\qry_x)$ would return, in game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use by~$\TestOracle$.  The $\HashOracle$ oracle also introduces a query counter~$c$, which is incremented whenever~$\HashOracle$ is called, either directly by~$A$ or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$ where~$\mathrm{Ans}[x]$ had not been previously defined by a~$\HashOracle(\qry_x)$ call.  \fixme{for BF proof, we can assume that $\TestOracle(\qry_x)$ is never made after a~$\HashOracle(\qry_x)$ call, because~$M$ is public.  And vice versa.  So the maximum value of~$c = q_T + q_H$.}  (Note that the maximum value of~$c$ is $q_T + q_H$.)  The set~$\calI$ contains a set of~$r$ distinct values from $\{1,2,\ldots,q_T+q_H\}$ and, intuitively, these are the game's ``guesses'' at the $\HashOracle$ queries that will result in a correctness error.  If these~$r$ guesses are incorrect, then a boolean flag~$\bad$ is set, although in game~$\game{4}$ the value of~$\bad$ has no effect on the games execution; in particular, $\game{4}$ does \emph{not} contain the boxed ``Return 0'' statement.

Games~$\game{4}$ and $\game{5}$ are identical except for this boxed statement.  In particular, game~$\game{5}$ returns 1 exactly when~$\game{4}$ would return 1 \emph{and} the boolean~$\bad$ would have remained false in~$\game{4}$.   This implies that~$\game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
$\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.

@@

Return $v$

@@

@@

@@

%\nudge $c \gets c + 1$\\
%\nudge for $j \in \{1,2,\ldots,k\}$\\
%\nudge $v_j \getsr [m]$\\
